\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.4in,bottom=0.4in,left=0.5in,right=0.5in]{geometry}
\linespread{0.92}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{amssymb}
\usepackage[colorlinks=true,urlcolor=themecolor,linkcolor=themecolor]{hyperref}
\usepackage{microtype}

% Maroon theme color used for the name-rule, section headings, and links.
\definecolor{themecolor}{HTML}{8A1F2B}

\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\pagestyle{empty}

% ---- Section formatting: maroon small-caps-ish bold heading + full-width rule ----
\titleformat{\section}
  {\color{themecolor}\normalfont\large\bfseries}
  {}{0em}{}[\color{themecolor}\titlerule\vspace{-2pt}]
\titlespacing*{\section}{0pt}{4pt}{2pt}

% ---- Helpers ----
% A two-column row on a single line: left text flush-left, right flush-right.
% Kept as one line (no wrap) so long entry headings match the original layout.
\newcommand{\tworow}[2]{\noindent\hbox to \linewidth{#1\hfill #2}\par}

% An entry heading: bold title (left) / plain location (right),
% then italic subtitle (left) / italic dates (right).
\newcommand{\entry}[4]{%
  \tworow{\textbf{#1}}{#2}%
  \vspace{1pt}%
  \tworow{\textit{#3}}{\textit{#4}}%
}

% A single-line entry: bold title (left) / plain dates (right).
\newcommand{\entryline}[2]{\tworow{\textbf{#1}}{#2}}

\setlist[itemize]{leftmargin=1.2em,topsep=1pt,itemsep=0.5pt,parsep=0pt}

\begin{document}

% ---------------- Header ----------------
\begin{center}
  {\huge\bfseries Dohun Kim}\\[4pt]
  {\small Weston, MA \quad$\bullet$\quad \href{mailto:dohunkimofficial@gmail.com}{\textcolor{black}{dohunkimofficial@gmail.com}} \quad$\bullet$\quad \href{https://dohunkim.xyz}{\textcolor{black}{dohunkim.xyz}} \quad$\bullet$\quad \href{https://github.com/genius0412}{\textcolor{black}{github.com/genius0412}}}
\end{center}

% ---------------- Education ----------------
\section{Education}
\entry{Weston High School}{Weston, MA}{High School Diploma (in progress) --- GPA 4.0 UW}{2024 -- Present}
\vspace{1pt}
\textbf{Coursework \& Exams:} AP Physics C: Mechanics and E\&M (A); AP Calculus BC (5); AP Computer Science A (5); AP Statistics (A); AP World History (A).
\vspace{1pt}

\entry{Hanyang University --- Gifted \& Talented Center for Informatics}{Seoul, South Korea}{Advanced Course in Informatics}{2020 -- 2021}
\begin{itemize}
  \item Graduated \#1 of 95 students and youngest in the Advanced cohort; only student selected for a 1-on-1 AI course under Prof.\ Ki Hyuk Sung.
\end{itemize}

% ---------------- Research & Publications ----------------
\section{Research \& Publications}
\tworow{\textbf{MIT PRIMES STEP --- Senior Group, Mathematics Research}}{\textit{2024 -- 2025}}
\vspace{1pt}
Co-authored two papers through MIT's selective research program, presenting original results in combinatorics and discrete mathematical structures.
\begin{itemize}
  \item \textit{Mathematics of Gozinta Boxes} --- \href{https://arxiv.org/abs/2508.18277}{arXiv:2508.18277}
  \item \textit{Chip-Firing in Infinite $k$-ary Trees} --- \href{https://arxiv.org/abs/2501.06675}{arXiv:2501.06675}
\end{itemize}

% ---------------- Leadership & Activities ----------------
\section{Leadership \& Activities}
\tworow{\textbf{FIRST Tech Challenge Robotics --- 22489 Galactic Narwhal Chicken Effect - Diamond}}{\textit{2024 -- 2026}}
\begin{itemize}
  \item Co-Captain (2025--2026) and team member (2024--2025); helped lead team strategy, build, and software.
  \item Team earned \textbf{2nd place for the Motivate Award} at the World Championship (Jemison Division).
  \item \textbf{Multinational Tech Invitational 2026:} won the \textbf{inaugural Mechatronics Synergy Award}.
  \item \textbf{Michiana Premier Event 2026:} Croft Division Finalist (alliance partner) and \textbf{1st place for the Control Award}.
  \item Designed the drivetrain and a clutch power-take-off lift system in open-source CAD (\href{https://cad.onshape.com/documents/8dbb6ec5b64ba5d9556668ce/w/7242710ea56febb23e213c1a/e/cf81280e74517a36b814bdf1}{Onshape}).
\end{itemize}
\vspace{1pt}
\tworow{\textbf{Volunteer FLL Mentor --- Teams ``Butterfly Effect'' \& ``LegoImpossible''}}{\textit{2024 -- 2026}}
\vspace{1pt}
\tworow{\textbf{Weston Robotics --- Planning Council \& Program-Wide Mentor}}{\textit{2026 -- Present}}
\vspace{1pt}
\tworow{\textbf{Weston Town Criers (A Cappella), Concert Choir \& Jazz Choir; Tennis}}{\textit{2024 -- Present}}
\begin{itemize}
  \item Featured soloist on ``500 Miles'' (2025--2026); selected for MMEA Senior Districts as bass (2024 \& 2025).
\end{itemize}

% ---------------- Honors & Awards ----------------
\section{Honors \& Awards}
\begin{itemize}
  \item \textbf{AMC 10A:} 141/150 (2024) \quad$\bullet$\quad \textbf{AIME II:} 9/15 (2025) \quad$\bullet$\quad MAML Olympiad Level 1: 2nd in Massachusetts (24/25).
  \item \textbf{USACO:} advanced to Gold Division, 900/1000 (2026) \quad$\bullet$\quad \textbf{Codeforces:} rating 1737.
  \item IMLEM: \#1 individual ranking with perfect scores across all 5 meets (2022--2023); MITIT 2023: 2nd, Beginner Division (team).
  \item Korean Olympiad in Informatics: Silver Award (National 2021; Regional 2021 \& 2022).
\end{itemize}

% ---------------- Selected Projects ----------------
\section{Selected Projects}
\begin{itemize}
  \item \textbf{DSIM} (\href{https://github.com/genius0412/dsim}{github.com/genius0412/dsim}) --- \textbf{Founder \& Main Programmer} of a real-time, 2-player browser robotics game: authoritative WebSocket server over a deterministic physics/scoring sim, 1v1/2v2 matchmaking, and a Glicko-2 ranked ladder. \textasciitilde39k lines of TypeScript/React; 527 passing tests.
  \item \textbf{Empower Initiative} (\href{https://empowerinit.org}{empowerinit.org}) --- Website Coordinator for a student-run tutoring nonprofit; built and maintain the organization's public site.
  \item \textbf{A11y Checker} (\href{https://youtu.be/qvqzYHCsRM8}{demo}) --- web accessibility checker; \textbf{2nd place}, 2021 Congressional App Challenge (Office of Rep.\ Katherine Clark).
  \item \textbf{Voya} (\href{https://voya.dohunkim.xyz}{voya.dohunkim.xyz}) --- interactive choose-your-own-adventure study game.
  \item \textbf{FTCDesign} (\href{https://www.ftcdesign.org}{ftcdesign.org}) --- Major Contributor to an open-source design resource for the FIRST Tech Challenge community.
  \item \textbf{Configlib} (\href{https://configlib.framer.website}{configlib.framer.website}) --- Major Contributor to an open-source configuration library for FTC robotics.
\end{itemize}

% ---------------- Skills ----------------
\section{Skills}
\textbf{Programming Languages:} C/C++, JavaScript/TypeScript, Python, Java\\
\textbf{Languages:} English (Fluent), Korean (Fluent), Spanish (Intermediate)\\
\textbf{Frameworks \& Tools:} React, Next.js, Onshape (CAD)

\end{document}
